Nonlinear system identification with neural networks for process control

### 2020-09-14 twccc.tex
add files for the talk.

	\begin{block}{Neural networks and system identification\footnote[frame]{\cite{hussain:1999, draeger:engell:ranke:1995, prasad:bequette:2003, eaton:rawlings:ungar:1994, bhat:minderman:mcavoy:wang:1990}}}
		\begin{itemize}
			\item \textbf{Black-box identification:} Estimate the entire predictive model ($x^+ =  f(x, u)$) from actuators to
			sensors using the data collected from open-loop identification experiments.
			\item \textbf{Hybrid model identification:} Model the dynamics from actuators to sensors using first-principle knowledge, and use
			neural networks to estimate the mismatch or any unmeasured disturbance dynamics.  
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}{Nonlinear HVAC example}
	\begin{align*}
	\dot{x} = Ax + Bg(u) + B_pp
	\end{align*}
	Nonlinearity between the valve (actuator) to the cooling duty. $x \in \{ T_{A1}, T_{C1}, T_{A2}, T_{C2} \}$, $u \in \{v_1, v_2\}$,
	and $p$ is the ambient temperature $T_a$ (disturbance).
	\pause
	\begin{figure}[!h]
		\centering
		\includegraphics[page = 5,width=0.6\textwidth]{plotshvacnn.pdf}
	\end{figure}
	\alert{Objective: Test the performance of linear MPC in regions of high plant-model mismatch.}
	\end{frame}

\begin{frame}{Linear MPC vs NN based MPC}
	\begin{figure}[!h]
		\centering
		\includegraphics[page = 2, width=0.48\textwidth]{plotshvacnn.pdf} \hfill
		\includegraphics[page = 3, width=0.48\textwidth]{plotshvacnn.pdf}
	\end{figure}

	\begin{itemize}
		\item NN trained on noisy open-loop system identification data (5000 samples).
		\item Change in ambient temperature at 10 hours, and setpoint changes in air-zone 
		temperatures at 50 and 100 hours. 
		\item The NN model provides superior closed-loop performance than the linear model.
	\end{itemize}
\end{frame}

>>>>

	\begin{block}{Neural networks and system identification\footnote[frame]{\cite{hussain:1999, draeger:engell:ranke:1995, prasad:bequette:2003, eaton:rawlings:ungar:1994, bhat:minderman:mcavoy:wang:1990}}}
		\begin{itemize}
			\item \textbf{Black-box identification:} Estimate the entire predictive model ($x^+ =  f(x, u)$) from actuators to
			sensors using data collected from open-loop identification experiments.
			\item \textbf{Hybrid model identification:} Model the dynamics from actuators to sensors using first-principle knowledge, and use
			neural networks (NNs) to estimate the mismatch or any unmeasured disturbance dynamics.  
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}{Nonlinear HVAC example}
	\begin{align*}
	\dot{x} = Ax + Bg(u) + B_pp
	\end{align*}
	Nonlinearity between the valve (actuator) to the cooling duty. $x \in \{ T_{A1}, T_{C1}, T_{A2}, T_{C2} \}$, $u \in \{v_1, v_2\}$,
	and $p$ is the ambient temperature $T_a$ (disturbance).
	\begin{figure}[!h]
		\centering
		\includegraphics[page = 5,width=0.6\textwidth]{plotshvacnn.pdf}
	\end{figure}
	\vspace{-0.1in}
	\begin{itemize}
		\item Test the performance of linear MPC in regions of high plant-model mismatch.
	\end{itemize}
\end{frame}

\begin{frame}{Linear MPC vs NN based MPC}
	\begin{figure}[!h]
		\centering
		\includegraphics[page = 2, width=0.48\textwidth]{plotshvacnn.pdf} \hfill
		\includegraphics[page = 3, width=0.48\textwidth]{plotshvacnn.pdf}
	\end{figure}
	\begin{itemize}
		\item NN trained on noisy open-loop system identification data (5000 samples).
		\item Change in ambient temperature at 10 hours, and setpoint changes in air-zone 
		temperatures at 50 and 100 hours. 
		\item The NN model provides superior closed-loop performance than the linear model.
	\end{itemize}
\end{frame}
